---
title: "IP PCA assignment"
output: html_document
---
##Business case
You are a Data analyst at Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax). Your project has been divided into four parts where you'll explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on your insights.

##Defining the question
Part 1: Dimensionality Reduction

This section of the project entails reducing your dataset to a low dimensional dataset using the t-SNE algorithm or PCA. You will be required to perform your analysis and provide insights gained from your analysis.

##Metrics of success
Our metrics of success will be determined by the selection of the features with the highest eigenvalues based on PCA reduction technique

##Below is the structure of our notebook:

 1.Reading the data
 2. Cleaning the data
 3. EDA
 4. Dimensionality reduction: PCA
 5. Conclusion
 
1. Step one
## Reading the data
```{r}
#Importing libraries
install.packages("tibble")
library(tibble)
```

```{r}
#Loading the data set
df_sales <- read.csv("Supermarket.csv")
```


```{r}
# Shape of the data
dim(df_sales)
# Our data has 1000 rows and 16 columns
```
```{r}
#Previewing our data
head(df_sales)

```
```{r}
# Summary of our data
summary(df_sales)
```
Step two
## Cleaning the data
```{r}
#Dealing with missing values
colSums(is.na(df_sales))
# There are no missing values in our dataset
```{r}

```

```

```{r}
#The dara types of our data
glimpse(df_sales)
```

```{r}
# Checking for duplicates
df_sales2 <- df_sales[duplicated(df_sales),]
dim(df_sales2)

df_sales <- unique(df_sales)
dim(df_sales)
#There are no duplicates
```

Selecting numerical columns only
```{r}
#Import libraries
install.packages("tidyverse")
suppressPackageStartupMessages(library(tidyverse))
library(dplyr)
df_salesnum <- dplyr::select_if(df_sales, is.numeric)

head(df_salesnum)
names(df_salesnum)_
glimpse(df_salesnum)
df<-subset(df_salesnum, select = -c(1,2) )
names(df)

```
Step three
##EDA
```{r}
#Import ggplot libraries
install.packages("ggplot2")
library(ggplot2)
```



```{r}
#Creating a barplot for customertypes
Branch<- df_sales$Branch
branch_freq <- table(Branch)
barplot(branch_freq)

#Branch A, B AND C have an equal distribution of customers
names(df_sales)
line<- df_sales$Product.line
line_freq <- table(line)
barplot(line_freq)
#Fashion accessories are the most purchased products followed by food and beverage and electrnic accessories

pay<- df_sales$Payment
pay_freq <- table(pay)
barplot(pay_freq)
#Most people pay with e-wallet and cash

```
```{r}
#Correlation
#use Hmisc package
install.packages("Hmisc")
library(Hmisc)

res <- rcorr(as.matrix(df))
corr <- data.frame(res$r)
corr

# get relationship between numerical variables

```

```
CORRELATION
```{r}
# get relationship between numerical variables
install.packages("corrplot")
suppressPackageStartupMessages(library(corrplot))
# Replacing nan values with zero
df2<-subset(df, select = -c(4) )
names(df2)
rev <- rcorr(as.matrix(df1))
corr <- data.frame(rev$r)
corr
```
Step four: Dimension Reduction: PCA
```{r}
df.pca <- prcomp(df2, center = TRUE, scale. = TRUE)
summary(df.pca)
```
PC1 explains 65% of the variance while PC2 and PC3 explains each 16% of the variance
```{r}
# Calling str() to have a look at your PCA object
# ---
# 
str(df.pca)

```
Plotting PCA
```{r}
# Installing our ggbiplot visualisation package
# 

library(devtools)
install_github("vqv/ggbiplot")

```

